---
title: "EAI: DA-LMP Pricing Model"
author: "Nicholas A. Coles and Eric S. Van Westering"
format: html
editor_options: 
  chunk_output_type: console
editor: 
  markdown: 
    wrap: 72
---

# hi,

Your previous weekend sensitivity analyses have been removed, as I have
helped you extract as much profit as I can.

If you want more recurring sensitivity analyses (henceforth called
'spotlight sensitivity analyses?), let Human Nick know. He has ensured
that the project is in currently set to the correct folder for file
deposits.\
\~ EAI

# Ongoing EAI threads (Last updated: Jan 17, NC)

N: Third day in a row that EAI's 65% PI is too conservative.

> N: No engineering-related explanation for why this is happening. EAI
> 65 hi trains the same way as all the other models.

N: I believe that there is preliminary evidence that EAI is
*systematically* too bearish when on high load days. Still good. But, in
my opinion, this means it's missing context.

> E: Yes - agree. This matches my gut check. So far I try to target
> wider bands on these days. If we can increase accuracy here it will
> give us more confidence to take bigger swings in the right scenarios
>
> > N: If you have ideas for additional variables, let me know. I have
> > been considering beefing up the models ever so slightly — but they
> > obviously won't do any better if they don't have the information
> > they need.

# Pricing calculator

```{r eval = F}
######################################
# note to user: adjust values below
######################################
target <- '2026-01-16'

buy.price <- 20
buy.quantity <- 10

sell.price <- 62
sell.quantity <- 150
######################################
# note to user: no more edits. hit the green play button to run chunk. everything below is Nick's
######################################

############################
# Nick code: create pricing sheet
############################
buy.sheet <-
  results %>% 
  filter(date_time == target) %>% 
  select(date_time,
         lo99 : hi15) %>% 
  pivot_longer(lo95 : hi65) %>% 
  extract(
    col   = name,                 # column to split
    into  = c("bound", "width"),     # new columns: hi/lo and numeric width
    regex = "^(hi|lo)(\\d+)$",       # capture 'hi' or 'lo' then digits
    convert = TRUE                   # converts width to integer
  ) %>% 
  select(width, 
         bound, value) %>% 
  mutate(value = value %>% 
           round(2),
         buy_price = buy.price %>% 
           round(2),
         buy_result = (value - buy_price) %>% 
           round(2),
         buy_quantity = buy.quantity %>% 
           round(2),
         buy_net = (buy_result * buy_quantity) %>% 
           round(2)
         ) %>% 
  tableGrob(rows = NULL,
            theme = 
              ttheme_minimal(
                colhead = list(bg_params = list(fill = "grey20"),
                               fg_params = list(col = "white")),
                
                core = list(
                  bg_params = 
                    list(fill = c('grey95', 'grey95',
                                  'grey85', 'grey85',
                                  'grey75', 'grey75',
                                  'grey65', 'grey65'))
                  )
                )
            )

sell.sheet <-
  results %>% 
  filter(date_time == target) %>% 
  select(date_time,
         lo99 : hi15) %>% 
  pivot_longer(lo95 : hi65) %>% 
  extract(
    col   = name,                 # column to split
    into  = c("bound", "width"),     # new columns: hi/lo and numeric width
    regex = "^(hi|lo)(\\d+)$",       # capture 'hi' or 'lo' then digits
    convert = TRUE                   # converts width to integer
  ) %>% 
  select(width, 
         bound, value) %>% 
  mutate(value = value %>% 
           round(2),
         sell_price = sell.price %>% 
           round(2),
         sell_result = (sell_price - value) %>% 
           round(2),
         sell_quantity = sell.quantity %>% 
           round(2),
         sell_net = (sell_result * sell_quantity) %>% 
           round(2)
         ) %>% 
  tableGrob(rows = NULL,
            theme = 
              ttheme_minimal(
                colhead = list(bg_params = list(fill = "grey20"),
                               fg_params = list(col = "white")),
                
                core = list(
                  bg_params = 
                    list(fill = c('grey95', 'grey95',
                                  'grey85', 'grey85',
                                  'grey75', 'grey75',
                                  'grey65', 'grey65'))
                  )
                )
            )

title <- ggdraw() +
  draw_label(paste0(target,
                    " pricing sheets"),
             fontface = 'bold', 
             x = 0.5, hjust = 0.5)

price.sheet.fig <-
  plot_grid(title, buy.sheet, sell.sheet,
          nrow = 3,
          rel_heights = c(.1, .45, .45))

save_plot(
  filename   = "price_sheet.pdf",
  plot       = price.sheet.fig,
  base_width = 8,    # landscape width
  base_height= 8,    # landscape height
  dpi        = 1000)

utils::browseURL("price_sheet.pdf")
```

```{r}
library(readxl)
df <- read_xls('eia.input.plus.xls')
```

# Re-run info through the models

```{r}
############################
# load libraries
############################
# time series autoML
library(h2o)
library(iForecast)
library(zoo)
library(slider)

# data processing
library(tidyverse)
library(readxl) 
library(janitor)
library(cowplot)
library(gridExtra)

# for pulling google drive data
library(googledrive)
library(readr)

# time series autoML
library(h2o)
library(iForecast)
library(zoo)
library(slider)

# data processing
library(tidyverse)
library(readxl)
library(janitor)
library(cowplot)
library(gridExtra)

# idiosyncratic settings
theme_set(theme_classic())
options(scipen = 999) # no sci notation
set.seed(1967)
Sys.setenv(TZ = "America/New_York")

############################
# re-open and process data
############################
df_lag <- df %>% 
  
  # clean variable names and structures
  clean_names() %>% 
  mutate(date_time = as.Date(date_time)) %>% 
  
  # add some variable suggestions from human Eric
  mutate(al.go =  
           rto_combined_bidclose_load_forecast_average / rto_combined_reg_total_gen_offline_capacity_average_latest,
         ml.go = rto_combined_bidclose_load_forecast_maximum / rto_combined_reg_total_gen_offline_capacity_average_latest,
         anl.go = rto_combined_net_load_forecast_bid_close_average / rto_combined_reg_total_gen_offline_capacity_average_latest,
         mnl.go = rto_combined_net_load_forecast_bid_close_maximum / rto_combined_reg_total_gen_offline_capacity_average_latest,
         # dclm.al = a_b_c_a_bge_bidclose_load_forecast_b_pepco_bidclose_load_forecast_c_dominion_bidclose_load_forecast_maximum / rto_combined_bidclose_load_forecast_average,
         malm.ml = mid_atlantic_region_bidclose_load_forecast_maximum / rto_combined_bidclose_load_forecast_maximum
         ) %>% 
  # create squared load predictor (at request of human Nick)
  mutate(load_sqr = rto_combined_bidclose_load_forecast_average ^ 2)

############################
# prepare function for adding 1, 2, 7-day lags of y and all exogenous vars
############################
lags <- c(1, 2, 7)

add_lags <- 
  function(data, 
           target, 
           exog, 
           lags) {
    
    out <- data
    
    # y lags
    for (L in lags) {
      out[[paste0(target, "_lag_", L)]] <- lag(out[[target]], L)
    }
    
    # exogenous lags
    for (col in exog) {
      for (L in lags) {
        out[[paste0(col, "_lag_", L)]] <- dplyr::lag(out[[col]], L)
      }
    }
    out
  }
  
df_lag <-
  # add lags
  add_lags(data = df_lag, 
           target = "western_hub_dalmp_average", 
           exog = setdiff(colnames(df_lag), 
                          c("date_time", 
                            "western_hub_dalmp_average",
                            "aep_dayton_hub_dalmp_average",
                            "n_illinois_hub_dalmp_average",
                            "dominion_hub_dalmp_average",
                            "eastern_hub_dalmp_average")), 
           lags = lags)

# Note to Nick: remember to review with Eric
df_lag$pjmiso_coalgen_hourly_average <- NA
df_lag$pjmiso_nucleargen_hourly_average <- NA

rm(lags, add_lags)

############################
# re-compile H20
############################
# Define length of test window (currently using k-fold for validation)
test_days  <- 50L
test_start  <- max(df_lag$date_time) - days(test_days)

# create splits (time-based)
trainvalid_df <- df_lag %>% filter(date_time <= test_start)
test_df  <- df_lag %>% filter(date_time > test_start)

trainvalid_df$date_time %>% min() 
trainvalid_df$date_time %>% max()

test_df$date_time %>% min()
test_df$date_time %>% max()

# Move to H2O
h2o.init()

trainvalid_h2o <- as.h2o(trainvalid_df)
test_h2o  <- as.h2o(test_df)

############################
# load pre-trained models
############################
dl_point <- h2o.loadModel('models/dl_point')
dl_50 <- h2o.loadModel('models/dl_50')

dl_99_lo <- h2o.loadModel('models/dl_99_lo')
dl_99_hi <- h2o.loadModel('models/dl_99_hi')

dl_95_lo <- h2o.loadModel('models/dl_95_lo')
dl_95_hi <- h2o.loadModel('models/dl_95_hi')

dl_85_lo <- h2o.loadModel('models/dl_85_lo')
dl_85_hi <- h2o.loadModel('models/dl_85_hi')

dl_75_lo <- h2o.loadModel('models/dl_75_lo')
dl_75_hi <- h2o.loadModel('models/dl_75_hi')

dl_65_lo <- h2o.loadModel('models/dl_65_lo')
dl_65_hi <- h2o.loadModel('models/dl_65_hi')

dl_55_lo <- h2o.loadModel('models/dl_55_lo')
dl_55_hi <- h2o.loadModel('models/dl_55_hi')

dl_45_lo <- h2o.loadModel('models/dl_45_lo')
dl_45_hi <- h2o.loadModel('models/dl_45_hi')

dl_35_lo <- h2o.loadModel('models/dl_35_lo')
dl_35_hi <- h2o.loadModel('models/dl_35_hi')

dl_25_lo <- h2o.loadModel('models/dl_25_lo')
dl_25_hi <- h2o.loadModel('models/dl_25_hi')

dl_15_lo <- h2o.loadModel('models/dl_15_lo')
dl_15_hi <- h2o.loadModel('models/dl_15_hi')

############################
# re-compile predictions
############################
pred_point <- h2o.predict(dl_point, test_h2o) %>% as.data.frame()

pred_50 <- h2o.predict(dl_50, test_h2o) %>% as.data.frame()

pred_99_lo <- h2o.predict(dl_99_lo, test_h2o) %>% as.data.frame()
pred_99_hi <- h2o.predict(dl_99_hi, test_h2o) %>% as.data.frame()

pred_95_lo <- h2o.predict(dl_95_lo, test_h2o) %>% as.data.frame()
pred_95_hi <- h2o.predict(dl_95_hi, test_h2o) %>% as.data.frame()

pred_85_lo <- h2o.predict(dl_85_lo, test_h2o) %>% as.data.frame()
pred_85_hi <- h2o.predict(dl_85_hi, test_h2o) %>% as.data.frame()

pred_75_lo <- h2o.predict(dl_75_lo, test_h2o) %>% as.data.frame()
pred_75_hi <- h2o.predict(dl_75_hi, test_h2o) %>% as.data.frame()

pred_65_lo <- h2o.predict(dl_65_lo, test_h2o) %>% as.data.frame()
pred_65_hi <- h2o.predict(dl_65_hi, test_h2o) %>% as.data.frame()

pred_55_lo <- h2o.predict(dl_55_lo, test_h2o) %>% as.data.frame()
pred_55_hi <- h2o.predict(dl_55_hi, test_h2o) %>% as.data.frame()

pred_45_lo <- h2o.predict(dl_45_lo, test_h2o) %>% as.data.frame()
pred_45_hi <- h2o.predict(dl_45_hi, test_h2o) %>% as.data.frame()

pred_35_lo <- h2o.predict(dl_35_lo, test_h2o) %>% as.data.frame()
pred_35_hi <- h2o.predict(dl_35_hi, test_h2o) %>% as.data.frame()

pred_25_lo <- h2o.predict(dl_25_lo, test_h2o) %>% as.data.frame()
pred_25_hi <- h2o.predict(dl_25_hi, test_h2o) %>% as.data.frame()

pred_15_lo <- h2o.predict(dl_15_lo, test_h2o) %>% as.data.frame()
pred_15_hi <- h2o.predict(dl_15_hi, test_h2o) %>% as.data.frame()

results <- test_df %>%
  select(date_time, western_hub_dalmp_average) %>%
  bind_cols(
    yhat   = pred_point$predict,
    lo99   = pred_99_lo$predict,
    hi99   = pred_99_hi$predict,
    lo95   = pred_95_lo$predict,
    hi95   = pred_95_hi$predict,
    lo85   = pred_85_lo$predict,
    hi85   = pred_85_hi$predict,
    lo75   = pred_75_lo$predict,
    hi75   = pred_75_hi$predict,
    lo65   = pred_65_lo$predict,
    hi65   = pred_65_hi$predict,
    lo55   = pred_55_lo$predict,
    hi55   = pred_55_hi$predict,
    lo45   = pred_45_lo$predict,
    hi45   = pred_45_hi$predict,
    lo35   = pred_35_lo$predict,
    hi35   = pred_35_hi$predict,
    lo25   = pred_25_lo$predict,
    hi25   = pred_25_hi$predict,
    lo15   = pred_15_lo$predict,
    hi15   = pred_15_hi$predict,
    med = pred_50$predict,
  )
```

# Generate full report

```{r}
############################
# time series
############################
# look at prediction interval accuracy
pi.acc <-
  results %>% 
  select(date_time, western_hub_dalmp_average, 
         lo95 : hi65) %>% 
  pivot_longer(lo95 : hi65) %>% 
  extract(
    col   = name,                 # column to split
    into  = c("bound", "width"),     # new columns: hi/lo and numeric width
    regex = "^(hi|lo)(\\d+)$",       # capture 'hi' or 'lo' then digits
    convert = TRUE                   # converts width to integer
  ) %>% 
  pivot_wider(names_from = 'bound',
              values_from = 'value') %>% 
  mutate(hit = 
           if_else(western_hub_dalmp_average > lo & western_hub_dalmp_average < hi,
                   true = 1,
                   false = 0)) %>% 
  group_by(width) %>% 
  summarise(m.hit = mean(hit,
                         na.rm = T) %>% 
              round(2) * 100)

# calculate summary notes
note1 <-
  abs(
    results$yhat - results$western_hub_dalmp_average
    ) %>% median(na.rm = T) %>% 
  round(2)

note1 <-
  paste0('EAI absolute median error (deployment): $',
         note1)

ts <- 
  ggplot(results, aes(x = date_time)) +
  
  # plot prediction w/ bands (mapped to fill for legend)
  geom_ribbon(aes(ymin = lo95, ymax = hi95, fill = "95% PI")) +
  geom_ribbon(aes(ymin = lo85, ymax = hi85, fill = "85% PI")) +
  geom_ribbon(aes(ymin = lo75, ymax = hi75, fill = "75% PI")) +
  geom_ribbon(aes(ymin = lo65, ymax = hi65, fill = "65% PI")) +
  
  # plot prediction line
  geom_line(aes(y = yhat, color = "Predicted"),
            linewidth = 1) +
  
  geom_line(aes(y = western_hub_dalmp_average, 
                color = "Actual"), 
            linewidth = 1,
            linetype = 'dotted') +
  
  # Manual scales to control colors and legend order
  scale_fill_manual(name = "Prediction Intervals",
                    values = c("95% PI" = "grey95", 
                               "85% PI" = "grey85", 
                               "75% PI" = "grey75", 
                               "65% PI" = "grey65"),
                    labels = c("95% PI" = 
                                 paste0("95% PI (actual coverage: ",
                                        pi.acc[pi.acc$width == 95, ]$m.hit,
                                        "%)"),
                               "85% PI" = 
                                 paste0("85% PI (actual coverage: ",
                                        pi.acc[pi.acc$width == 85, ]$m.hit,
                                        "%)"), 
                               "75% PI" = 
                                 paste0("75% PI (actual coverage: ",
                                        pi.acc[pi.acc$width == 75, ]$m.hit,
                                        "%)"), 
                               "65% PI" = 
                                 paste0("65% PI (actual coverage: ",
                                        pi.acc[pi.acc$width == 65, ]$m.hit,
                                        "%)")
                               )
                    ) +
  scale_color_manual(name = "Data Type",
                     values = c("Predicted" = "black", 
                                "Actual" = "black")
                     ) +
  labs(y = 'DA-LMP',
       x  = 'date',
       title = note1) +
  scale_x_date(date_breaks = "1 day", date_labels = "%b %d") +

  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    # Positions legend inside the top-right of the plot area
    legend.position = c(0.95, 0.99),
    legend.justification = c("right", "top"),
    legend.background = element_rect(fill = alpha("white", 0.5))
  )

rm(note1)

############################
# price distribution curve: t
############################
# using quantiles, dynamically identify xmin and xmax of figures
plot.xmin <- min(results$lo99, na.rm = T) - 5

plot.xmax <- quantile(results$western_hub_dalmp_average,
                      .99,
                      na.rm = T)

# goal: get probability density curves
pb.t.input <-
  results %>% 
  filter(date_time == Sys.Date() + 1)

# identify probability positions positions
prob.positions <-
  c(0.005,
    0.025,
    0.075,
    0.125,
    0.175, 
    0.225,
    0.275,
    0.325,
    0.375,
    0.425,
    .5,
    0.575,
    0.625,
    0.675,
    0.725,
    0.775,
    0.825,
    0.875,
    0.925,
    0.975,
    0.995)

# identify values at positions
prices <-
  c(pb.t.input$lo99,
    pb.t.input$lo95,
    pb.t.input$lo85,
    pb.t.input$lo75,
    pb.t.input$lo65,
    pb.t.input$lo55,
    pb.t.input$lo45,
    pb.t.input$lo35,
    pb.t.input$lo25,
    pb.t.input$lo15,
    pb.t.input$med,
    pb.t.input$hi15,
    pb.t.input$hi25,
    pb.t.input$hi35,
    pb.t.input$hi45,
    pb.t.input$hi55,
    pb.t.input$hi65,
    pb.t.input$hi75,
    pb.t.input$hi85,
    pb.t.input$hi95,
    pb.t.input$hi99)

pd.t0 <-
  ggplot(data = data_frame(prob.positions = prob.positions,
                         prices = prices),
       aes(x = prices)) +
  geom_vline(data = pb.t.input,
             aes(xintercept = yhat),
             linetype = 'dotted') +
  geom_density(aes(weight = prob.positions),
               bw = 10) +
  labs(x = 'DA-LMP',
       y = 'density',
       title = paste0(pb.t.input$date_time,
                      " prediction : $",
                      pb.t.input$yhat[1] %>% round(2),
                     " / MWh"
                      )) +
  scale_x_continuous(limits = c(plot.xmin, 
                                plot.xmax)) +
  
  # 95% PI
  geom_segment(data = pb.t.input,
               aes(x = lo95, 
                   y = .035, 
                   xend = hi95, 
                   yend = .035),
               color = 'grey75'
               ) +
  
  geom_label(data = pb.t.input,
             aes(x = (lo95 + hi95) / 2, 
                 y = .035, 
                 label = "95%"),
             color = 'grey75',
             size = 3.2) +
  
  geom_text(data = pb.t.input,
            aes(x = lo95, 
                y = .035, 
                label = lo95 %>% round(2)),
            size = 3.2,
            hjust = 1.25,
            color = 'grey75') +
  
  geom_text(data = pb.t.input,
            aes(x = hi95, 
                y = .035, 
                label = hi95 %>% round(2)),
            size = 3.2,
            hjust = -.25,
            color = 'grey75') +
  
  # 85% PI
  geom_segment(data = pb.t.input,
               aes(x = lo85, 
                   y = .04, 
                   xend = hi85, 
                   yend = .04),
               color = 'grey65') +
  
  geom_label(data = pb.t.input,
             aes(x = (lo85 + hi85) / 2, 
                 y = .04, 
                 label = "85%"),
             size = 3.2,
             color = 'grey65') +
  
  geom_text(data = pb.t.input,
            aes(x = lo85, 
                y = .04, 
                label = lo85 %>% round(2)),
            size = 3.2,
            hjust = 1.25,
            color = 'grey65') +
  
  geom_text(data = pb.t.input,
            aes(x = hi85, 
                y = .04, 
                label = hi85 %>% round(2)),
            size = 3.2,
            hjust = -.25,
            color = 'grey65') +
  
  # 75% PI
  geom_segment(data = pb.t.input,
               aes(x = lo75, 
                   y = .045, 
                   xend = hi75, 
                   yend = .045),
               color = 'grey55') +
  
  geom_label(data = pb.t.input,
             aes(x = (lo75 + hi75) / 2, 
                 y = .045, 
                 label = "75%"),
             size = 3.2,
             color = 'grey55') +
  
  geom_text(data = pb.t.input,
            aes(x = lo75, 
                y = .045, 
                label = lo75 %>% round(2)),
            size = 3.2,
            hjust = 1.25,
            color = 'grey55') +
  
  geom_text(data = pb.t.input,
            aes(x = hi75, 
                y = .045, 
                label = hi75 %>% round(2)),
            size = 3.2,
            hjust = -.25,
            color = 'grey55')

############################
# price distribution curve: t1
############################
# goal: get probability density curves
pb.t.input <-
  results %>% 
  filter(date_time == Sys.Date() + 2)

# identify probability positions positions
prob.positions <-
  c(0.005,
    0.025,
    0.075,
    0.125,
    0.175, 
    0.225,
    0.275,
    0.325,
    0.375,
    0.425,
    .5,
    0.575,
    0.625,
    0.675,
    0.725,
    0.775,
    0.825,
    0.875,
    0.925,
    0.975,
    0.995)

# identify values at positions
prices <-
  c(pb.t.input$lo99,
    pb.t.input$lo95,
    pb.t.input$lo85,
    pb.t.input$lo75,
    pb.t.input$lo65,
    pb.t.input$lo55,
    pb.t.input$lo45,
    pb.t.input$lo35,
    pb.t.input$lo25,
    pb.t.input$lo15,
    pb.t.input$med,
    pb.t.input$hi15,
    pb.t.input$hi25,
    pb.t.input$hi35,
    pb.t.input$hi45,
    pb.t.input$hi55,
    pb.t.input$hi65,
    pb.t.input$hi75,
    pb.t.input$hi85,
    pb.t.input$hi95,
    pb.t.input$hi99)

pd.t1 <-
  ggplot(data = data_frame(prob.positions = prob.positions,
                         prices = prices),
       aes(x = prices)) +
  geom_vline(data = pb.t.input,
             aes(xintercept = yhat),
             linetype = 'dotted') +
  geom_density(aes(weight = prob.positions),
               bw = 10) +
  labs(x = 'DA-LMP',
       y = 'density',
       title = paste0(pb.t.input$date_time,
                      " prediction : $",
                      pb.t.input$yhat[1] %>% round(2),
                     " / MWh"
                      )) +
  scale_x_continuous(limits = c(plot.xmin, 
                                plot.xmax)) +
  
  # 95% PI
  geom_segment(data = pb.t.input,
               aes(x = lo95, 
                   y = .035, 
                   xend = hi95, 
                   yend = .035),
               color = 'grey75'
               ) +
  
  geom_label(data = pb.t.input,
             aes(x = (lo95 + hi95) / 2, 
                 y = .035, 
                 label = "95%"),
             color = 'grey75',
             size = 3.2) +
  
  geom_text(data = pb.t.input,
            aes(x = lo95, 
                y = .035, 
                label = lo95 %>% round(2)),
            size = 3.2,
            hjust = 1.25,
            color = 'grey75') +
  
  geom_text(data = pb.t.input,
            aes(x = hi95, 
                y = .035, 
                label = hi95 %>% round(2)),
            size = 3.2,
            hjust = -.25,
            color = 'grey75') +
  
  # 85% PI
  geom_segment(data = pb.t.input,
               aes(x = lo85, 
                   y = .04, 
                   xend = hi85, 
                   yend = .04),
               color = 'grey65') +
  
  geom_label(data = pb.t.input,
             aes(x = (lo85 + hi85) / 2, 
                 y = .04, 
                 label = "85%"),
             size = 3.2,
             color = 'grey65') +
  
  geom_text(data = pb.t.input,
            aes(x = lo85, 
                y = .04, 
                label = lo85 %>% round(2)),
            size = 3.2,
            hjust = 1.25,
            color = 'grey65') +
  
  geom_text(data = pb.t.input,
            aes(x = hi85, 
                y = .04, 
                label = hi85 %>% round(2)),
            size = 3.2,
            hjust = -.25,
            color = 'grey65') +
  
  # 75% PI
  geom_segment(data = pb.t.input,
               aes(x = lo75, 
                   y = .045, 
                   xend = hi75, 
                   yend = .045),
               color = 'grey55') +
  
  geom_label(data = pb.t.input,
             aes(x = (lo75 + hi75) / 2, 
                 y = .045, 
                 label = "75%"),
             size = 3.2,
             color = 'grey55') +
  
  geom_text(data = pb.t.input,
            aes(x = lo75, 
                y = .045, 
                label = lo75 %>% round(2)),
            size = 3.2,
            hjust = 1.25,
            color = 'grey55') +
  
  geom_text(data = pb.t.input,
            aes(x = hi75, 
                y = .045, 
                label = hi75 %>% round(2)),
            size = 3.2,
            hjust = -.25,
            color = 'grey55')

############################
# price distribution curve: t2
############################
# goal: get probability density curves
pb.t.input <-
  results %>% 
  filter(date_time == Sys.Date() + 3)

# identify probability positions positions
prob.positions <-
  c(0.005,
    0.025,
    0.075,
    0.125,
    0.175, 
    0.225,
    0.275,
    0.325,
    0.375,
    0.425,
    .5,
    0.575,
    0.625,
    0.675,
    0.725,
    0.775,
    0.825,
    0.875,
    0.925,
    0.975,
    0.995)

# identify values at positions
prices <-
  c(pb.t.input$lo99,
    pb.t.input$lo95,
    pb.t.input$lo85,
    pb.t.input$lo75,
    pb.t.input$lo65,
    pb.t.input$lo55,
    pb.t.input$lo45,
    pb.t.input$lo35,
    pb.t.input$lo25,
    pb.t.input$lo15,
    pb.t.input$med,
    pb.t.input$hi15,
    pb.t.input$hi25,
    pb.t.input$hi35,
    pb.t.input$hi45,
    pb.t.input$hi55,
    pb.t.input$hi65,
    pb.t.input$hi75,
    pb.t.input$hi85,
    pb.t.input$hi95,
    pb.t.input$hi99)

pd.t2 <-
  ggplot(data = data_frame(prob.positions = prob.positions,
                         prices = prices),
       aes(x = prices)) +
  geom_vline(data = pb.t.input,
             aes(xintercept = yhat),
             linetype = 'dotted') +
  geom_density(aes(weight = prob.positions),
               bw = 10) +
  labs(x = 'DA-LMP',
       y = 'density',
       title = paste0(pb.t.input$date_time,
                      " prediction : $",
                      pb.t.input$yhat[1] %>% round(2),
                     " / MWh"
                      )) +
  scale_x_continuous(limits = c(plot.xmin, 
                                plot.xmax)) +
  
  # 95% PI
  geom_segment(data = pb.t.input,
               aes(x = lo95, 
                   y = .035, 
                   xend = hi95, 
                   yend = .035),
               color = 'grey75'
               ) +
  
  geom_label(data = pb.t.input,
             aes(x = (lo95 + hi95) / 2, 
                 y = .035, 
                 label = "95%"),
             color = 'grey75',
             size = 3.2) +
  
  geom_text(data = pb.t.input,
            aes(x = lo95, 
                y = .035, 
                label = lo95 %>% round(2)),
            size = 3.2,
            hjust = 1.25,
            color = 'grey75') +
  
  geom_text(data = pb.t.input,
            aes(x = hi95, 
                y = .035, 
                label = hi95 %>% round(2)),
            size = 3.2,
            hjust = -.25,
            color = 'grey75') +
  
  # 85% PI
  geom_segment(data = pb.t.input,
               aes(x = lo85, 
                   y = .04, 
                   xend = hi85, 
                   yend = .04),
               color = 'grey65') +
  
  geom_label(data = pb.t.input,
             aes(x = (lo85 + hi85) / 2, 
                 y = .04, 
                 label = "85%"),
             size = 3.2,
             color = 'grey65') +
  
  geom_text(data = pb.t.input,
            aes(x = lo85, 
                y = .04, 
                label = lo85 %>% round(2)),
            size = 3.2,
            hjust = 1.25,
            color = 'grey65') +
  
  geom_text(data = pb.t.input,
            aes(x = hi85, 
                y = .04, 
                label = hi85 %>% round(2)),
            size = 3.2,
            hjust = -.25,
            color = 'grey65') +
  
  # 75% PI
  geom_segment(data = pb.t.input,
               aes(x = lo75, 
                   y = .045, 
                   xend = hi75, 
                   yend = .045),
               color = 'grey55') +
  
  geom_label(data = pb.t.input,
             aes(x = (lo75 + hi75) / 2, 
                 y = .045, 
                 label = "75%"),
             size = 3.2,
             color = 'grey55') +
  
  geom_text(data = pb.t.input,
            aes(x = lo75, 
                y = .045, 
                label = lo75 %>% round(2)),
            size = 3.2,
            hjust = 1.25,
            color = 'grey55') +
  
  geom_text(data = pb.t.input,
            aes(x = hi75, 
                y = .045, 
                label = hi75 %>% round(2)),
            size = 3.2,
            hjust = -.25,
            color = 'grey55')

############################
# price distribution curve: t3
############################
# goal: get probability density curves
pb.t.input <-
  results %>% 
  filter(date_time == Sys.Date() + 4)

# identify probability positions positions
prob.positions <-
  c(0.005,
    0.025,
    0.075,
    0.125,
    0.175, 
    0.225,
    0.275,
    0.325,
    0.375,
    0.425,
    .5,
    0.575,
    0.625,
    0.675,
    0.725,
    0.775,
    0.825,
    0.875,
    0.925,
    0.975,
    0.995)

# identify values at positions
prices <-
  c(pb.t.input$lo99,
    pb.t.input$lo95,
    pb.t.input$lo85,
    pb.t.input$lo75,
    pb.t.input$lo65,
    pb.t.input$lo55,
    pb.t.input$lo45,
    pb.t.input$lo35,
    pb.t.input$lo25,
    pb.t.input$lo15,
    pb.t.input$med,
    pb.t.input$hi15,
    pb.t.input$hi25,
    pb.t.input$hi35,
    pb.t.input$hi45,
    pb.t.input$hi55,
    pb.t.input$hi65,
    pb.t.input$hi75,
    pb.t.input$hi85,
    pb.t.input$hi95,
    pb.t.input$hi99)

pd.t3 <-
  ggplot(data = data_frame(prob.positions = prob.positions,
                         prices = prices),
       aes(x = prices)) +
  geom_vline(data = pb.t.input,
             aes(xintercept = yhat),
             linetype = 'dotted') +
  geom_density(aes(weight = prob.positions),
               bw = 10) +
  labs(x = 'DA-LMP',
       y = 'density',
       title = paste0(pb.t.input$date_time,
                      " prediction : $",
                      pb.t.input$yhat[1] %>% round(2),
                     " / MWh"
                      )) +
  scale_x_continuous(limits = c(plot.xmin, 
                                plot.xmax)) +
  # 95% PI
  geom_segment(data = pb.t.input,
               aes(x = lo95, 
                   y = .035, 
                   xend = hi95, 
                   yend = .035),
               color = 'grey75'
               ) +
  
  geom_label(data = pb.t.input,
             aes(x = (lo95 + hi95) / 2, 
                 y = .035, 
                 label = "95%"),
             color = 'grey75',
             size = 3.2) +
  
  geom_text(data = pb.t.input,
            aes(x = lo95, 
                y = .035, 
                label = lo95 %>% round(2)),
            size = 3.2,
            hjust = 1.25,
            color = 'grey75') +
  
  geom_text(data = pb.t.input,
            aes(x = hi95, 
                y = .035, 
                label = hi95 %>% round(2)),
            size = 3.2,
            hjust = -.25,
            color = 'grey75') +
  
  # 85% PI
  geom_segment(data = pb.t.input,
               aes(x = lo85, 
                   y = .04, 
                   xend = hi85, 
                   yend = .04),
               color = 'grey65') +
  
  geom_label(data = pb.t.input,
             aes(x = (lo85 + hi85) / 2, 
                 y = .04, 
                 label = "85%"),
             size = 3.2,
             color = 'grey65') +
  
  geom_text(data = pb.t.input,
            aes(x = lo85, 
                y = .04, 
                label = lo85 %>% round(2)),
            size = 3.2,
            hjust = 1.25,
            color = 'grey65') +
  
  geom_text(data = pb.t.input,
            aes(x = hi85, 
                y = .04, 
                label = hi85 %>% round(2)),
            size = 3.2,
            hjust = -.25,
            color = 'grey65') +
  
  # 75% PI
  geom_segment(data = pb.t.input,
               aes(x = lo75, 
                   y = .045, 
                   xend = hi75, 
                   yend = .045),
               color = 'grey55') +
  
  geom_label(data = pb.t.input,
             aes(x = (lo75 + hi75) / 2, 
                 y = .045, 
                 label = "75%"),
             size = 3.2,
             color = 'grey55') +
  
  geom_text(data = pb.t.input,
            aes(x = lo75, 
                y = .045, 
                label = lo75 %>% round(2)),
            size = 3.2,
            hjust = 1.25,
            color = 'grey55') +
  
  geom_text(data = pb.t.input,
            aes(x = hi75, 
                y = .045, 
                label = hi75 %>% round(2)),
            size = 3.2,
            hjust = -.25,
            color = 'grey55')

############################
# price distribution curve: t4
############################
# goal: get probability density curves
pb.t.input <-
  results %>% 
  filter(date_time == Sys.Date() + 5)

# identify probability positions positions
prob.positions <-
  c(0.005,
    0.025,
    0.075,
    0.125,
    0.175, 
    0.225,
    0.275,
    0.325,
    0.375,
    0.425,
    .5,
    0.575,
    0.625,
    0.675,
    0.725,
    0.775,
    0.825,
    0.875,
    0.925,
    0.975,
    0.995)

# identify values at positions
prices <-
  c(pb.t.input$lo99,
    pb.t.input$lo95,
    pb.t.input$lo85,
    pb.t.input$lo75,
    pb.t.input$lo65,
    pb.t.input$lo55,
    pb.t.input$lo45,
    pb.t.input$lo35,
    pb.t.input$lo25,
    pb.t.input$lo15,
    pb.t.input$med,
    pb.t.input$hi15,
    pb.t.input$hi25,
    pb.t.input$hi35,
    pb.t.input$hi45,
    pb.t.input$hi55,
    pb.t.input$hi65,
    pb.t.input$hi75,
    pb.t.input$hi85,
    pb.t.input$hi95,
    pb.t.input$hi99)

pd.t4 <-
  ggplot(data = data_frame(prob.positions = prob.positions,
                         prices = prices),
       aes(x = prices)) +
  geom_vline(data = pb.t.input,
             aes(xintercept = yhat),
             linetype = 'dotted') +
  geom_density(aes(weight = prob.positions),
               bw = 10) +
  labs(x = 'DA-LMP',
       y = 'density',
       title = paste0(pb.t.input$date_time,
                      " prediction : $",
                      pb.t.input$yhat[1] %>% round(2),
                     " / MWh"
                      )) +
  scale_x_continuous(limits = c(plot.xmin, 
                                plot.xmax)) +
  # 95% PI
  geom_segment(data = pb.t.input,
               aes(x = lo95, 
                   y = .035, 
                   xend = hi95, 
                   yend = .035),
               color = 'grey75'
               ) +
  
  geom_label(data = pb.t.input,
             aes(x = (lo95 + hi95) / 2, 
                 y = .035, 
                 label = "95%"),
             color = 'grey75',
             size = 3.2) +
  
  geom_text(data = pb.t.input,
            aes(x = lo95, 
                y = .035, 
                label = lo95 %>% round(2)),
            size = 3.2,
            hjust = 1.25,
            color = 'grey75') +
  
  geom_text(data = pb.t.input,
            aes(x = hi95, 
                y = .035, 
                label = hi95 %>% round(2)),
            size = 3.2,
            hjust = -.25,
            color = 'grey75') +
  
  # 85% PI
  geom_segment(data = pb.t.input,
               aes(x = lo85, 
                   y = .04, 
                   xend = hi85, 
                   yend = .04),
               color = 'grey65') +
  
  geom_label(data = pb.t.input,
             aes(x = (lo85 + hi85) / 2, 
                 y = .04, 
                 label = "85%"),
             size = 3.2,
             color = 'grey65') +
  
  geom_text(data = pb.t.input,
            aes(x = lo85, 
                y = .04, 
                label = lo85 %>% round(2)),
            size = 3.2,
            hjust = 1.25,
            color = 'grey65') +
  
  geom_text(data = pb.t.input,
            aes(x = hi85, 
                y = .04, 
                label = hi85 %>% round(2)),
            size = 3.2,
            hjust = -.25,
            color = 'grey65') +
  
  # 75% PI
  geom_segment(data = pb.t.input,
               aes(x = lo75, 
                   y = .045, 
                   xend = hi75, 
                   yend = .045),
               color = 'grey55') +
  
  geom_label(data = pb.t.input,
             aes(x = (lo75 + hi75) / 2, 
                 y = .045, 
                 label = "75%"),
             size = 3.2,
             color = 'grey55') +
  
  geom_text(data = pb.t.input,
            aes(x = lo75, 
                y = .045, 
                label = lo75 %>% round(2)),
            size = 3.2,
            hjust = 1.25,
            color = 'grey55') +
  
  geom_text(data = pb.t.input,
            aes(x = hi75, 
                y = .045, 
                label = hi75 %>% round(2)),
            size = 3.2,
            hjust = -.25,
            color = 'grey55')

############################
# price distribution curve: t5
############################
# goal: get probability density curves
pb.t.input <-
  results %>% 
  filter(date_time == Sys.Date() + 6)

# identify probability positions positions
prob.positions <-
  c(0.005,
    0.025,
    0.075,
    0.125,
    0.175, 
    0.225,
    0.275,
    0.325,
    0.375,
    0.425,
    .5,
    0.575,
    0.625,
    0.675,
    0.725,
    0.775,
    0.825,
    0.875,
    0.925,
    0.975,
    0.995)

# identify values at positions
prices <-
  c(pb.t.input$lo99,
    pb.t.input$lo95,
    pb.t.input$lo85,
    pb.t.input$lo75,
    pb.t.input$lo65,
    pb.t.input$lo55,
    pb.t.input$lo45,
    pb.t.input$lo35,
    pb.t.input$lo25,
    pb.t.input$lo15,
    pb.t.input$med,
    pb.t.input$hi15,
    pb.t.input$hi25,
    pb.t.input$hi35,
    pb.t.input$hi45,
    pb.t.input$hi55,
    pb.t.input$hi65,
    pb.t.input$hi75,
    pb.t.input$hi85,
    pb.t.input$hi95,
    pb.t.input$hi99)

pd.t5 <-
  ggplot(data = data_frame(prob.positions = prob.positions,
                         prices = prices),
       aes(x = prices)) +
  geom_vline(data = pb.t.input,
             aes(xintercept = yhat),
             linetype = 'dotted') +
  geom_density(aes(weight = prob.positions),
               bw = 10) +
  labs(x = 'DA-LMP',
       y = 'density',
       title = paste0(pb.t.input$date_time,
                      " prediction : $",
                      pb.t.input$yhat[1] %>% round(2),
                     " / MWh"
                      )) +
  scale_x_continuous(limits = c(plot.xmin, 
                                plot.xmax)) +
  #95% PI
  geom_segment(data = pb.t.input,
               aes(x = lo95, 
                   y = .035, 
                   xend = hi95, 
                   yend = .035),
               color = 'grey75'
               ) +
  
  geom_label(data = pb.t.input,
             aes(x = (lo95 + hi95) / 2, 
                 y = .035, 
                 label = "95%"),
             color = 'grey75',
             size = 3.2) +
  
  geom_text(data = pb.t.input,
            aes(x = lo95, 
                y = .035, 
                label = lo95 %>% round(2)),
            size = 3.2,
            hjust = 1.25,
            color = 'grey75') +
  
  geom_text(data = pb.t.input,
            aes(x = hi95, 
                y = .035, 
                label = hi95 %>% round(2)),
            size = 3.2,
            hjust = -.25,
            color = 'grey75') +
  
  #85% PI
  geom_segment(data = pb.t.input,
               aes(x = lo85, 
                   y = .04, 
                   xend = hi85, 
                   yend = .04),
               color = 'grey65') +
  
  geom_label(data = pb.t.input,
             aes(x = (lo85 + hi85) / 2, 
                 y = .04, 
                 label = "85%"),
             size = 3.2,
             color = 'grey65') +
  
  geom_text(data = pb.t.input,
            aes(x = lo85, 
                y = .04, 
                label = lo85 %>% round(2)),
            size = 3.2,
            hjust = 1.25,
            color = 'grey65') +
  
  geom_text(data = pb.t.input,
            aes(x = hi85, 
                y = .04, 
                label = hi85 %>% round(2)),
            size = 3.2,
            hjust = -.25,
            color = 'grey65') +
  
  #75% PI
  geom_segment(data = pb.t.input,
               aes(x = lo75, 
                   y = .045, 
                   xend = hi75, 
                   yend = .045),
               color = 'grey55') +
  
  geom_label(data = pb.t.input,
             aes(x = (lo75 + hi75) / 2, 
                 y = .045, 
                 label = "75%"),
             size = 3.2,
             color = 'grey55') +
  
  geom_text(data = pb.t.input,
            aes(x = lo75, 
                y = .045, 
                label = lo75 %>% round(2)),
            size = 3.2,
            hjust = 1.25,
            color = 'grey55') +
  
  geom_text(data = pb.t.input,
            aes(x = hi75, 
                y = .045, 
                label = hi75 %>% round(2)),
            size = 3.2,
            hjust = -.25,
            color = 'grey55')

############################
# prediction band input
############################
# target
pb.t.input <-
  results %>% 
  filter(date_time == Sys.Date() +1) %>% 
  pivot_longer(lo95 : hi65) %>% 
  extract(
    col   = name,                 # column to split
    into  = c("bound", "width"),     # new columns: hi/lo and numeric width
    regex = "^(hi|lo)(\\d+)$",       # capture 'hi' or 'lo' then digits
    convert = TRUE                   # converts width to integer
  ) %>% 
  pivot_wider(names_from = 'bound',
              values_from = 'value')

pb.tp1.input <-
  results %>% 
  filter(date_time == Sys.Date() +2) %>% 
  pivot_longer(lo95 : hi65) %>% 
  extract(
    col   = name,                 # column to split
    into  = c("bound", "width"),     # new columns: hi/lo and numeric width
    regex = "^(hi|lo)(\\d+)$",       # capture 'hi' or 'lo' then digits
    convert = TRUE                   # converts width to integer
  ) %>% 
  pivot_wider(names_from = 'bound',
              values_from = 'value')

pb.tp2.input <-
  results %>% 
  filter(date_time == Sys.Date() +3) %>% 
  pivot_longer(lo95 : hi65) %>% 
  extract(
    col   = name,                 # column to split
    into  = c("bound", "width"),     # new columns: hi/lo and numeric width
    regex = "^(hi|lo)(\\d+)$",       # capture 'hi' or 'lo' then digits
    convert = TRUE                   # converts width to integer
  ) %>% 
  pivot_wider(names_from = 'bound',
              values_from = 'value')

pb.tp3.input <-
  results %>% 
  filter(date_time == Sys.Date() +4) %>% 
  pivot_longer(lo95 : hi65) %>% 
  extract(
    col   = name,                 # column to split
    into  = c("bound", "width"),     # new columns: hi/lo and numeric width
    regex = "^(hi|lo)(\\d+)$",       # capture 'hi' or 'lo' then digits
    convert = TRUE                   # converts width to integer
  ) %>% 
  pivot_wider(names_from = 'bound',
              values_from = 'value')

pb.tp4.input <-
 results %>% 
 filter(date_time == Sys.Date() +5) %>% 
 pivot_longer(lo95 : hi65) %>% 
 extract(
   col   = name,                 # column to split
   into  = c("bound", "width"),     # new columns: hi/lo and numeric width
   regex = "^(hi|lo)(\\d+)$",       # capture 'hi' or 'lo' then digits
   convert = TRUE                   # converts width to integer
 ) %>% 
 pivot_wider(names_from = 'bound',
             values_from = 'value')

pb.tp5.input <-
 results %>% 
 filter(date_time == Sys.Date() + 6) %>% 
 pivot_longer(lo95 : hi65) %>% 
 extract(
   col   = name,                 # column to split
   into  = c("bound", "width"),     # new columns: hi/lo and numeric width
   regex = "^(hi|lo)(\\d+)$",       # capture 'hi' or 'lo' then digits
   convert = TRUE                   # converts width to integer
 ) %>% 
 pivot_wider(names_from = 'bound',
             values_from = 'value')

############################
# prediction band plot
############################
pb.t <- 
  ggplot(data = pb.t.input,
         aes(x = width)) +
  geom_ribbon(aes(ymin = lo, 
                  ymax = hi), 
              fill = "grey95") +
  geom_hline(yintercept = pb.t.input$yhat[1],
             linetype = 'dotted') +
  scale_x_continuous(breaks = c(65, 75, 85, 95)) +
  labs(x = 'prediction interval width',
       y = 'predicted DA-LMP',
       title = paste(pb.t.input$date_time[1],
                     "prediction : $",
                     pb.t.input$yhat[1] %>% round(3),
                     " / MWh"))

pb.tp1 <- 
  ggplot(data = pb.tp1.input,
         aes(x = width)) +
  geom_ribbon(aes(ymin = lo, 
                  ymax = hi), 
              fill = "grey95") +
  geom_hline(yintercept = pb.tp1.input$yhat[1],
             linetype = 'dotted') +
  scale_x_continuous(breaks = c(65, 75, 85, 95)) +
  labs(x = 'prediction interval width',
       y = 'predicted DA-LMP',
       title = paste(pb.tp1.input$date_time[1],
                     "prediction : $",
                     pb.tp1.input$yhat[1] %>% round(2),
                     " / MWh"))

pb.tp2 <- 
  ggplot(data = pb.tp2.input,
         aes(x = width)) +
  geom_ribbon(aes(ymin = lo, 
                  ymax = hi), 
              fill = "grey95") +
  geom_hline(yintercept = pb.tp2.input$yhat[1],
             linetype = 'dotted') +
  scale_x_continuous(breaks = c(65, 75, 85, 95)) +
  labs(x = 'prediction interval width',
       y = 'predicted DA-LMP',
       title = paste(pb.tp2.input$date_time[1],
                     "prediction : $",
                     pb.tp2.input$yhat[1] %>% round(2),
                     " / MWh"))

pb.tp3 <- 
  ggplot(data = pb.tp3.input,
         aes(x = width)) +
  geom_ribbon(aes(ymin = lo, 
                  ymax = hi), 
              fill = "grey95") +
  geom_hline(yintercept = pb.tp3.input$yhat[1],
             linetype = 'dotted') +
  scale_x_continuous(breaks = c(65, 75, 85, 95)) +
  labs(x = 'prediction interval width',
       y = 'predicted DA-LMP',
       title = paste(pb.tp3.input$date_time[1],
                     "prediction : $",
                     pb.tp3.input$yhat[1] %>% round(2),
                     " / MWh"))

  pb.tp4 <- 
    ggplot(data = pb.tp4.input,
           aes(x = width)) +
    geom_ribbon(aes(ymin = lo, 
                    ymax = hi), 
                fill = "grey95") +
    geom_hline(yintercept = pb.tp4.input$yhat[1],
               linetype = 'dotted') +
    scale_x_continuous(breaks = c(65, 75, 85, 95)) +
    labs(x = 'prediction interval width',
         y = 'predicted DA-LMP',
         title = paste(pb.tp4.input$date_time[1],
                       "prediction : $",
                       pb.tp4.input$yhat[1] %>% round(2),
                       " / MWh"))

############################
# prepare prediction band summaries
############################
summary <-
  results %>% 
  pivot_longer(lo95 : hi65) %>% 
  extract(
    col   = name,                 # column to split
    into  = c("bound", "width"),     # new columns: hi/lo and numeric width
    regex = "^(hi|lo)(\\d+)$",       # capture 'hi' or 'lo' then digits
    convert = TRUE                   # converts width to integer
  ) %>% 
  pivot_wider(names_from = 'bound',
              values_from = 'value') %>% 
  mutate(abs.err = abs(western_hub_dalmp_average - yhat),
         hit = 
           if_else(western_hub_dalmp_average > lo & western_hub_dalmp_average < hi,
                   true = 1,
                   false = 0))

summary2 <- summary %>% 
  group_by(width) %>% 
  summarise(accuracy = mean(hit,
                            na.rm = T),
            accuracy = round(accuracy, 3)) %>% 
  rename('prediction interval width' = 'width',
         'tested accuracy' = 'accuracy')

############################
# create prediction band plots
############################
s.t <- summary %>% 
  filter(as.character(date_time) == Sys.Date() +1) %>% 
  select(width, lo, hi) %>% 
  mutate(lo = round(lo, 2),
         hi = round(hi, 2)) %>% 
  rename('prediction interval width' = 'width') %>% 
  right_join(summary2,
             by = 'prediction interval width') %>% 
  select(`prediction interval width`, `tested accuracy`, lo, hi) %>% 
  tableGrob(rows = NULL)

s.t1 <- summary %>% 
  filter(as.character(date_time) == 
           Sys.Date() +2) %>% 
  select(width, lo, hi) %>% 
  mutate(lo = round(lo, 2),
         hi = round(hi, 2)) %>% 
  rename('prediction interval width' = 'width') %>% 
  right_join(summary2,
             by = 'prediction interval width') %>% 
  select(`prediction interval width`, `tested accuracy`, lo, hi) %>% 
  tableGrob(rows = NULL)

s.t2 <- summary %>% 
  filter(as.character(date_time) == 
           Sys.Date() +3) %>% 
  select(width, lo, hi) %>% 
  mutate(lo = round(lo, 2),
         hi = round(hi, 2)) %>% 
  rename('prediction interval width' = 'width') %>% 
  right_join(summary2,
             by = 'prediction interval width') %>% 
  select(`prediction interval width`, `tested accuracy`, lo, hi) %>% 
  tableGrob(rows = NULL)

s.t3 <- summary %>% 
  filter(as.character(date_time) == 
           Sys.Date() +4) %>% 
  select(width, lo, hi) %>% 
  mutate(lo = round(lo, 2),
         hi = round(hi, 2)) %>% 
  rename('prediction interval width' = 'width') %>% 
  right_join(summary2,
             by = 'prediction interval width') %>% 
  select(`prediction interval width`, `tested accuracy`, lo, hi) %>% 
  tableGrob(rows = NULL)

s.t4 <- summary %>% 
  filter(as.character(date_time) == 
           Sys.Date() +5) %>% 
  select(width, lo, hi) %>% 
  mutate(lo = round(lo, 2),
         hi = round(hi, 2)) %>% 
  rename('prediction interval width' = 'width') %>% 
  right_join(summary2,
             by = 'prediction interval width') %>% 
  select(`prediction interval width`, `tested accuracy`, lo, hi) %>% 
  tableGrob(rows = NULL)

s.t5 <- summary %>% 
  filter(as.character(date_time) == 
           Sys.Date() + 6) %>% 
  select(width, lo, hi) %>% 
  mutate(lo = round(lo, 2),
         hi = round(hi, 2)) %>% 
  rename('prediction interval width' = 'width') %>% 
  right_join(summary2,
             by = 'prediction interval width') %>% 
  select(`prediction interval width`, `tested accuracy`, lo, hi) %>% 
  tableGrob(rows = NULL)

############################
# Tomorrow: pricing sensitivity analysis
############################
# load sensitivity analysis
load.sens <-
  lapply(X = c((-15000),(-10000), (-5000),
               15000,     10000,    5000
               ),
         function(x){
           
           c.test_df <-
             df_lag %>% 
             # filter by target date
             filter(date_time == Sys.Date() + 1) %>% 
             
             # replace with counterfactual value
             mutate(rto_combined_bidclose_load_forecast_average =
                      rto_combined_bidclose_load_forecast_average + x)
           
           c.test_h2o  <- as.h2o(c.test_df)
           
           # re-compile predictions
           c.pred_point <- h2o.predict(dl_point, c.test_h2o) %>% as.data.frame()
           
           c.pred_50 <- h2o.predict(dl_50, c.test_h2o) %>% as.data.frame()
           
           c.pred_99_lo <- h2o.predict(dl_99_lo, c.test_h2o) %>% as.data.frame()
           c.pred_99_hi <- h2o.predict(dl_99_hi, c.test_h2o) %>% as.data.frame()
           
           c.pred_95_lo <- h2o.predict(dl_95_lo, c.test_h2o) %>% as.data.frame()
           c.pred_95_hi <- h2o.predict(dl_95_hi, c.test_h2o) %>% as.data.frame()
           
           c.pred_85_lo <- h2o.predict(dl_85_lo, c.test_h2o) %>% as.data.frame()
           c.pred_85_hi <- h2o.predict(dl_85_hi, c.test_h2o) %>% as.data.frame()
           
           c.pred_75_lo <- h2o.predict(dl_75_lo, c.test_h2o) %>% as.data.frame()
           c.pred_75_hi <- h2o.predict(dl_75_hi, c.test_h2o) %>% as.data.frame()
           
           c.pred_65_lo <- h2o.predict(dl_65_lo, c.test_h2o) %>% as.data.frame()
           c.pred_65_hi <- h2o.predict(dl_65_hi, c.test_h2o) %>% as.data.frame()
           
           c.pred_55_lo <- h2o.predict(dl_55_lo, c.test_h2o) %>% as.data.frame()
           c.pred_55_hi <- h2o.predict(dl_55_hi, c.test_h2o) %>% as.data.frame()
           
           c.pred_45_lo <- h2o.predict(dl_45_lo, c.test_h2o) %>% as.data.frame()
           c.pred_45_hi <- h2o.predict(dl_45_hi, c.test_h2o) %>% as.data.frame()
           
           c.pred_35_lo <- h2o.predict(dl_35_lo, c.test_h2o) %>% as.data.frame()
           c.pred_35_hi <- h2o.predict(dl_35_hi, c.test_h2o) %>% as.data.frame()
           
           c.pred_25_lo <- h2o.predict(dl_25_lo, c.test_h2o) %>% as.data.frame()
           c.pred_25_hi <- h2o.predict(dl_25_hi, c.test_h2o) %>% as.data.frame()
           
           c.pred_15_lo <- h2o.predict(dl_15_lo, c.test_h2o) %>% as.data.frame()
           c.pred_15_hi <- h2o.predict(dl_15_hi, c.test_h2o) %>% as.data.frame()
           
           c.results <- c.test_df %>%
             select(date_time, western_hub_dalmp_average) %>%
             bind_cols(
               yhat   = c.pred_point$predict,
               lo99   = c.pred_99_lo$predict,
               hi99   = c.pred_99_hi$predict,
               lo95   = c.pred_95_lo$predict,
               hi95   = c.pred_95_hi$predict,
               lo85   = c.pred_85_lo$predict,
               hi85   = c.pred_85_hi$predict,
               lo75   = c.pred_75_lo$predict,
               hi75   = c.pred_75_hi$predict,
               lo65   = c.pred_65_lo$predict,
               hi65   = c.pred_65_hi$predict,
               lo55   = c.pred_55_lo$predict,
               hi55   = c.pred_55_hi$predict,
               lo45   = c.pred_45_lo$predict,
               hi45   = c.pred_45_hi$predict,
               lo35   = c.pred_35_lo$predict,
               hi35   = c.pred_35_hi$predict,
               lo25   = c.pred_25_lo$predict,
               hi25   = c.pred_25_hi$predict,
               lo15   = c.pred_15_lo$predict,
               hi15   = c.pred_15_hi$predict,
               med = c.pred_50$predict,
             )
           
           # prepare prediction band summaries
           c.summary <-
             c.results %>% 
             pivot_longer(lo95 : hi65) %>% 
             extract(
               col   = name,                 # column to split
               into  = c("bound", "width"),     # new columns: hi/lo and numeric width
               regex = "^(hi|lo)(\\d+)$",       # capture 'hi' or 'lo' then digits
               convert = TRUE                   # converts width to integer
             ) %>% 
             pivot_wider(names_from = 'bound',
                         values_from = 'value') %>% 
             mutate(load_delta = x) %>% 
             select(load_delta, width, lo, hi) %>% 
             mutate(lo = round(lo, 2),
                    hi = round(hi, 2))
           
           return(c.summary)
           
         }
         )
load.sens <- bind_rows(load.sens) %>% 
  arrange(width, load_delta) %>% 
  tableGrob(rows = NULL)

# gas sensitivity analysis
gas.sens <-
  lapply(X = c((-1.5),(-1.0), (-0.5),
                 1.5,   1.0,    0.5
  ),
  function(x){
    
    c.test_df <-
      df_lag %>% 
      # filter by target date
      filter(date_time == Sys.Date() + 1) %>% 
      
      # replace with counterfactual value
      mutate(tetco_m3_gasprice_average =
               tetco_m3_gasprice_average + x,
             henry_gasprice_average =
               henry_gasprice_average + x)
    
    c.test_h2o  <- as.h2o(c.test_df)
    
    # re-compile predictions
    c.pred_point <- h2o.predict(dl_point, c.test_h2o) %>% as.data.frame()
    
    c.pred_50 <- h2o.predict(dl_50, c.test_h2o) %>% as.data.frame()
    
    c.pred_99_lo <- h2o.predict(dl_99_lo, c.test_h2o) %>% as.data.frame()
    c.pred_99_hi <- h2o.predict(dl_99_hi, c.test_h2o) %>% as.data.frame()
    
    c.pred_95_lo <- h2o.predict(dl_95_lo, c.test_h2o) %>% as.data.frame()
    c.pred_95_hi <- h2o.predict(dl_95_hi, c.test_h2o) %>% as.data.frame()
    
    c.pred_85_lo <- h2o.predict(dl_85_lo, c.test_h2o) %>% as.data.frame()
    c.pred_85_hi <- h2o.predict(dl_85_hi, c.test_h2o) %>% as.data.frame()
    
    c.pred_75_lo <- h2o.predict(dl_75_lo, c.test_h2o) %>% as.data.frame()
    c.pred_75_hi <- h2o.predict(dl_75_hi, c.test_h2o) %>% as.data.frame()
    
    c.pred_65_lo <- h2o.predict(dl_65_lo, c.test_h2o) %>% as.data.frame()
    c.pred_65_hi <- h2o.predict(dl_65_hi, c.test_h2o) %>% as.data.frame()
    
    c.pred_55_lo <- h2o.predict(dl_55_lo, c.test_h2o) %>% as.data.frame()
    c.pred_55_hi <- h2o.predict(dl_55_hi, c.test_h2o) %>% as.data.frame()
    
    c.pred_45_lo <- h2o.predict(dl_45_lo, c.test_h2o) %>% as.data.frame()
    c.pred_45_hi <- h2o.predict(dl_45_hi, c.test_h2o) %>% as.data.frame()
    
    c.pred_35_lo <- h2o.predict(dl_35_lo, c.test_h2o) %>% as.data.frame()
    c.pred_35_hi <- h2o.predict(dl_35_hi, c.test_h2o) %>% as.data.frame()
    
    c.pred_25_lo <- h2o.predict(dl_25_lo, c.test_h2o) %>% as.data.frame()
    c.pred_25_hi <- h2o.predict(dl_25_hi, c.test_h2o) %>% as.data.frame()
    
    c.pred_15_lo <- h2o.predict(dl_15_lo, c.test_h2o) %>% as.data.frame()
    c.pred_15_hi <- h2o.predict(dl_15_hi, c.test_h2o) %>% as.data.frame()
    
    c.results <- c.test_df %>%
      select(date_time, western_hub_dalmp_average) %>%
      bind_cols(
        yhat   = c.pred_point$predict,
        lo99   = c.pred_99_lo$predict,
        hi99   = c.pred_99_hi$predict,
        lo95   = c.pred_95_lo$predict,
        hi95   = c.pred_95_hi$predict,
        lo85   = c.pred_85_lo$predict,
        hi85   = c.pred_85_hi$predict,
        lo75   = c.pred_75_lo$predict,
        hi75   = c.pred_75_hi$predict,
        lo65   = c.pred_65_lo$predict,
        hi65   = c.pred_65_hi$predict,
        lo55   = c.pred_55_lo$predict,
        hi55   = c.pred_55_hi$predict,
        lo45   = c.pred_45_lo$predict,
        hi45   = c.pred_45_hi$predict,
        lo35   = c.pred_35_lo$predict,
        hi35   = c.pred_35_hi$predict,
        lo25   = c.pred_25_lo$predict,
        hi25   = c.pred_25_hi$predict,
        lo15   = c.pred_15_lo$predict,
        hi15   = c.pred_15_hi$predict,
        med = c.pred_50$predict,
      )
    
    # prepare prediction band summaries
    c.summary <-
      c.results %>% 
      pivot_longer(lo95 : hi65) %>% 
      extract(
        col   = name,                 # column to split
        into  = c("bound", "width"),     # new columns: hi/lo and numeric width
        regex = "^(hi|lo)(\\d+)$",       # capture 'hi' or 'lo' then digits
        convert = TRUE                   # converts width to integer
      ) %>% 
      pivot_wider(names_from = 'bound',
                  values_from = 'value') %>% 
      mutate(gas_delta = x) %>% 
      select(gas_delta, width, lo, hi) %>% 
      mutate(lo = round(lo, 2),
             hi = round(hi, 2))
    
    return(c.summary)
    
  }
  )

gas.sens <- bind_rows(gas.sens) %>% 
  arrange(width, gas_delta) %>% 
  tableGrob(rows = NULL)

# solar sensitivity analysis
solar.sens <-
  lapply(X = c((-1500),(-1000), (-500),
                 1500,   1000,    500
  ),
  function(x){
    
    c.test_df <-
      df_lag %>% 
      # filter by target date
      filter(date_time == Sys.Date() + 1) %>% 
      
      # replace with counterfactual value
      mutate(rto_combined_bidclose_solarfcst_hourly_average =
               rto_combined_bidclose_solarfcst_hourly_average + x)
    
    c.test_h2o  <- as.h2o(c.test_df)
    
    # re-compile predictions
    c.pred_point <- h2o.predict(dl_point, c.test_h2o) %>% as.data.frame()
    
    c.pred_50 <- h2o.predict(dl_50, c.test_h2o) %>% as.data.frame()
    
    c.pred_99_lo <- h2o.predict(dl_99_lo, c.test_h2o) %>% as.data.frame()
    c.pred_99_hi <- h2o.predict(dl_99_hi, c.test_h2o) %>% as.data.frame()
    
    c.pred_95_lo <- h2o.predict(dl_95_lo, c.test_h2o) %>% as.data.frame()
    c.pred_95_hi <- h2o.predict(dl_95_hi, c.test_h2o) %>% as.data.frame()
    
    c.pred_85_lo <- h2o.predict(dl_85_lo, c.test_h2o) %>% as.data.frame()
    c.pred_85_hi <- h2o.predict(dl_85_hi, c.test_h2o) %>% as.data.frame()
    
    c.pred_75_lo <- h2o.predict(dl_75_lo, c.test_h2o) %>% as.data.frame()
    c.pred_75_hi <- h2o.predict(dl_75_hi, c.test_h2o) %>% as.data.frame()
    
    c.pred_65_lo <- h2o.predict(dl_65_lo, c.test_h2o) %>% as.data.frame()
    c.pred_65_hi <- h2o.predict(dl_65_hi, c.test_h2o) %>% as.data.frame()
    
    c.pred_55_lo <- h2o.predict(dl_55_lo, c.test_h2o) %>% as.data.frame()
    c.pred_55_hi <- h2o.predict(dl_55_hi, c.test_h2o) %>% as.data.frame()
    
    c.pred_45_lo <- h2o.predict(dl_45_lo, c.test_h2o) %>% as.data.frame()
    c.pred_45_hi <- h2o.predict(dl_45_hi, c.test_h2o) %>% as.data.frame()
    
    c.pred_35_lo <- h2o.predict(dl_35_lo, c.test_h2o) %>% as.data.frame()
    c.pred_35_hi <- h2o.predict(dl_35_hi, c.test_h2o) %>% as.data.frame()
    
    c.pred_25_lo <- h2o.predict(dl_25_lo, c.test_h2o) %>% as.data.frame()
    c.pred_25_hi <- h2o.predict(dl_25_hi, c.test_h2o) %>% as.data.frame()
    
    c.pred_15_lo <- h2o.predict(dl_15_lo, c.test_h2o) %>% as.data.frame()
    c.pred_15_hi <- h2o.predict(dl_15_hi, c.test_h2o) %>% as.data.frame()
    
    c.results <- c.test_df %>%
      select(date_time, western_hub_dalmp_average) %>%
      bind_cols(
        yhat   = c.pred_point$predict,
        lo99   = c.pred_99_lo$predict,
        hi99   = c.pred_99_hi$predict,
        lo95   = c.pred_95_lo$predict,
        hi95   = c.pred_95_hi$predict,
        lo85   = c.pred_85_lo$predict,
        hi85   = c.pred_85_hi$predict,
        lo75   = c.pred_75_lo$predict,
        hi75   = c.pred_75_hi$predict,
        lo65   = c.pred_65_lo$predict,
        hi65   = c.pred_65_hi$predict,
        lo55   = c.pred_55_lo$predict,
        hi55   = c.pred_55_hi$predict,
        lo45   = c.pred_45_lo$predict,
        hi45   = c.pred_45_hi$predict,
        lo35   = c.pred_35_lo$predict,
        hi35   = c.pred_35_hi$predict,
        lo25   = c.pred_25_lo$predict,
        hi25   = c.pred_25_hi$predict,
        lo15   = c.pred_15_lo$predict,
        hi15   = c.pred_15_hi$predict,
        med = c.pred_50$predict,
      )
    
    # prepare prediction band summaries
    c.summary <-
      c.results %>% 
      pivot_longer(lo95 : hi65) %>% 
      extract(
        col   = name,                 # column to split
        into  = c("bound", "width"),     # new columns: hi/lo and numeric width
        regex = "^(hi|lo)(\\d+)$",       # capture 'hi' or 'lo' then digits
        convert = TRUE                   # converts width to integer
      ) %>% 
      pivot_wider(names_from = 'bound',
                  values_from = 'value') %>% 
      mutate(solar_delta = x) %>% 
      select(solar_delta, width, lo, hi) %>% 
      mutate(lo = round(lo, 2),
             hi = round(hi, 2))
    
    return(c.summary)
    
  }
  )

solar.sens <- bind_rows(solar.sens) %>% 
  arrange(width, solar_delta) %>% tableGrob(rows = NULL)

# wind sensitivity analysis
wind.sens <-
  lapply(X = c((-3000),(-2000), (-1000),
                 1000,   2000,    3000
  ),
  function(x){
    
    c.test_df <-
      df_lag %>% 
      # filter by target date
      filter(date_time == Sys.Date() + 1) %>% 
      
      # replace with counterfactual value
      mutate(rto_combined_bidclose_winddata_stf_average =
               rto_combined_bidclose_winddata_stf_average + x)
    
    c.test_h2o  <- as.h2o(c.test_df)
    
    # re-compile predictions
    c.pred_point <- h2o.predict(dl_point, c.test_h2o) %>% as.data.frame()
    
    c.pred_50 <- h2o.predict(dl_50, c.test_h2o) %>% as.data.frame()
    
    c.pred_99_lo <- h2o.predict(dl_99_lo, c.test_h2o) %>% as.data.frame()
    c.pred_99_hi <- h2o.predict(dl_99_hi, c.test_h2o) %>% as.data.frame()
    
    c.pred_95_lo <- h2o.predict(dl_95_lo, c.test_h2o) %>% as.data.frame()
    c.pred_95_hi <- h2o.predict(dl_95_hi, c.test_h2o) %>% as.data.frame()
    
    c.pred_85_lo <- h2o.predict(dl_85_lo, c.test_h2o) %>% as.data.frame()
    c.pred_85_hi <- h2o.predict(dl_85_hi, c.test_h2o) %>% as.data.frame()
    
    c.pred_75_lo <- h2o.predict(dl_75_lo, c.test_h2o) %>% as.data.frame()
    c.pred_75_hi <- h2o.predict(dl_75_hi, c.test_h2o) %>% as.data.frame()
    
    c.pred_65_lo <- h2o.predict(dl_65_lo, c.test_h2o) %>% as.data.frame()
    c.pred_65_hi <- h2o.predict(dl_65_hi, c.test_h2o) %>% as.data.frame()
    
    c.pred_55_lo <- h2o.predict(dl_55_lo, c.test_h2o) %>% as.data.frame()
    c.pred_55_hi <- h2o.predict(dl_55_hi, c.test_h2o) %>% as.data.frame()
    
    c.pred_45_lo <- h2o.predict(dl_45_lo, c.test_h2o) %>% as.data.frame()
    c.pred_45_hi <- h2o.predict(dl_45_hi, c.test_h2o) %>% as.data.frame()
    
    c.pred_35_lo <- h2o.predict(dl_35_lo, c.test_h2o) %>% as.data.frame()
    c.pred_35_hi <- h2o.predict(dl_35_hi, c.test_h2o) %>% as.data.frame()
    
    c.pred_25_lo <- h2o.predict(dl_25_lo, c.test_h2o) %>% as.data.frame()
    c.pred_25_hi <- h2o.predict(dl_25_hi, c.test_h2o) %>% as.data.frame()
    
    c.pred_15_lo <- h2o.predict(dl_15_lo, c.test_h2o) %>% as.data.frame()
    c.pred_15_hi <- h2o.predict(dl_15_hi, c.test_h2o) %>% as.data.frame()
    
    c.results <- c.test_df %>%
      select(date_time, western_hub_dalmp_average) %>%
      bind_cols(
        yhat   = c.pred_point$predict,
        lo99   = c.pred_99_lo$predict,
        hi99   = c.pred_99_hi$predict,
        lo95   = c.pred_95_lo$predict,
        hi95   = c.pred_95_hi$predict,
        lo85   = c.pred_85_lo$predict,
        hi85   = c.pred_85_hi$predict,
        lo75   = c.pred_75_lo$predict,
        hi75   = c.pred_75_hi$predict,
        lo65   = c.pred_65_lo$predict,
        hi65   = c.pred_65_hi$predict,
        lo55   = c.pred_55_lo$predict,
        hi55   = c.pred_55_hi$predict,
        lo45   = c.pred_45_lo$predict,
        hi45   = c.pred_45_hi$predict,
        lo35   = c.pred_35_lo$predict,
        hi35   = c.pred_35_hi$predict,
        lo25   = c.pred_25_lo$predict,
        hi25   = c.pred_25_hi$predict,
        lo15   = c.pred_15_lo$predict,
        hi15   = c.pred_15_hi$predict,
        med = c.pred_50$predict,
      )
    
    # prepare prediction band summaries
    c.summary <-
      c.results %>% 
      pivot_longer(lo95 : hi65) %>% 
      extract(
        col   = name,                 # column to split
        into  = c("bound", "width"),     # new columns: hi/lo and numeric width
        regex = "^(hi|lo)(\\d+)$",       # capture 'hi' or 'lo' then digits
        convert = TRUE                   # converts width to integer
      ) %>% 
      pivot_wider(names_from = 'bound',
                  values_from = 'value') %>% 
      mutate(wind_delta = x) %>% 
      select(wind_delta, width, lo, hi) %>% 
      mutate(lo = round(lo, 2),
             hi = round(hi, 2))
    
    return(c.summary)
    
  }
  )

wind.sens <- bind_rows(wind.sens) %>% 
  arrange(width, wind_delta) %>% tableGrob(rows = NULL)

title <-
  ggdraw() +
  draw_label(paste0((Sys.Date() + 1),
                    " sensitivity analyses"),
             fontface = 'bold', 
             x = 0.5, hjust = 0.5)

############################
# Create plot
############################
sum.plot <-
  plot_grid(ts,
          plot_grid(pd.t0, s.t, 
                    ncol = 2,
                    rel_widths = c(.6, .4)),
          plot_grid(pd.t1, s.t1, 
                    ncol = 2,
                    rel_widths = c(.6, .4)),
          plot_grid(pd.t2, s.t2, 
                    ncol = 2,
                    rel_widths = c(.6, .4)),
          plot_grid(pd.t3, s.t3, 
                    ncol = 2,
                    rel_widths = c(.6, .4)),
          plot_grid(pd.t4, s.t4, 
                    ncol = 2,
                    rel_widths = c(.6, .4)),
          plot_grid(pd.t5, s.t5, 
                    ncol = 2,
                    rel_widths = c(.6, .4)),
          plot_grid(title,
                    plot_grid(load.sens, gas.sens, 
                              solar.sens, wind.sens,
                              ncol = 4),
                    nrow = 2,
                    rel_heights = c(1, 25)),
          nrow = 8,
          rel_heights = c(1, rep(.7, 6), 2),
          scale = 0.97)

save_plot(
  filename   = "EAI_Report_Full.pdf",
  plot       = sum.plot,
  base_width = 15,    # landscape width
  base_height= 30,    # landscape height
  limitsize = F,
  dpi        = 1000)

utils::browseURL("EAI_Report_Full.pdf")
```

# Old reminders

-   I am trained, validated, and tested on my ability to predict how PJM
    West solves prices given the inputted 'state of the grid'.

-   If you believe future states of the grid are misprojected (or have
    since changed), you should adjust the inputs to best match your
    expectations.

-   If you want to know how a change in the state of the grid might
    affect your pricing expectations and positions, you can screenshot
    the output, adjust the inputs, re-run, and compare.
